Reconstructing Propositional Proofs in Type Theory

### 2017-10-23 paper/sections/proof-reconstruction/clausify.tex
[ paper ] lots of changes.
[ paper ] fixed conjunct example.

In the following \Metis \TSTP derivation, we see an example where
\clausify expands the formula \texttt{norm0} by using distributive
laws included in the conjunctive normal form conversion.

@@

\begin{remark}
The \clausify rule is often preceded by \canonicalize.
Both rules perform \emph{Clausification} that introduces
into the problem axioms and definitions in the domain of the solution.
The clausification algorithms is mainly described on paper by
\citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
\end{remark}

>>>>

\begin{myexample}
In the following \Metis \TSTP derivation, we see how
\clausify expands the\texttt{norm0} formula to get \texttt{norm1} formula
by using distributive laws included in the conjunctive normal form conversion.

@@

\begin{myremark}
The \clausify rule is often preceded by \canonicalize.
Both rules perform \emph{Clausification} that introduces
into the problem axioms and definitions in the domain of the solution.
The clausification algorithms is mainly described on paper by
\citeauthor{Sutcliffe1996}~\cite{Sutcliffe1996}.
\end{myremark}

### 2017-10-23 paper/sections/proof-reconstruction/conjunct.tex
[ paper ] lots of changes.
[ paper ] fixed conjunct example.

The \conjunct rule extracts from a
conjunction one of its conjuncts. This rule is a generalization of the
projection rules for the conjunction connective as the
following \TSTP excerpt shows. In the first formula \verb!p1!, \verb!p & q & (r | ~ p)!, is a left-associative conjunction. \conjunct extracts \verb!q! from the \verb!p1! conjunction by using twice left projection (∧-proj₁).

@@

@@

\begin{proof}\hspace{2cm}\\
\begin{itemize}
\item[$\bullet$] Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
Then, we get the desire conclusion by applying the $\fsubst$ lemma.
\item[$\bullet$] Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct~φ_{i}~ψ$ for some $i = 1,\ 2$, then,

>>>>

The \conjunct rule extracts from a
conjunction one of its conjuncts. This rule is a generalization of the
projection rules for the conjunction connective as the
following \TSTP excerpt shows.

\begin{myexample}\hspace{10cm}

@@

In the first formula, \verb!p & q & (r | ~ p)!, we find a left-associative
conjunction named \verb!p1!.
\conjunct extracts \verb!q! from the \verb!p1! using a left
projection (∧-proj₁) follow by a right projection (∧-proj₂).
\conjunct extracts \verb!r | ~ p! by using right projection
on \verb!p1!.
\end{myexample}

@@

\begin{proof}\hspace{10cm}
\begin{itemize}
\item[$\bullet$] Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
Then, we get the desire conclusion by applying the $\fsubst$ lemma.
\item[$\bullet$] Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct~φ_{i}~ψ$ for some $i = 1,\ 2$, then,
